Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle

### 2022-04-05 finalReportPres.tex
Update finalReportPres.tex
I added to the introduction slides of the final report presentation
Update finalReportPres.tex
I added to the Neural Network Modeling slide for the brake system

\begin{frame}{Introduction}{Problem Statement}
  \begin{block}{Problem Statement}
    \begin{LARGE}

    \end{LARGE}
  \end{block}
  \pause
  \begin{block}{Proposed Solution}
    \begin{LARGE}

    \end{LARGE}
  \end{block}
\end{frame}

@@

\begin{frame}{Neural Network Modeling}{Brake System}

@@

\begin{frame}{Conclusions and Future Work}
  \begin{block}{Conclusions}
    \begin{itemize}
      \item 
    \end{itemize}
  \end{block}
  \begin{block}{Future Work}
    \begin{itemize}
      \item 
    \end{itemize}
  \end{block}
\end{frame}

>>>>

\begin{frame}{Introduction}{Problem Statement}
  \begin{block}{Problem Statement}
    \begin{Large}
    		Model autonomous vehicle subsystems for a Lexus platform
    \end{Large}
  \end{block}
  \pause
  \begin{block}{Proposed Solution}
    \begin{Large}
    		Use MATLAB's System Identification Toolbox to create models
    \end{Large}
  \end{block}
\end{frame}

@@

\begin{frame}{Neural Network Modeling}{Brake System}
  \begin{block}{Modeling Process}
    		\begin{itemize}
    			\item Trained using data from the first brake log
    			\item Model tested with data from the second brake log
    		\end{itemize}
    		\begin{figure}[h]
			\includegraphics[width=0.48\linewidth]{figs/img/brake_new_neuralNetworkFig}
			\includegraphics[width=0.48\linewidth]{figs/img/brake_new_neuralNetworkFigLog2Test}
\end{figure}
%    		\begin{figure}[H]
%    		\centering \includegraphics[width=.48\linewidth , height=.37\textheight]{figs/img/newBrakeSimulinkBlock.jpg}
%    		\end{figure}
  \end{block}
\end{frame}

@@

\begin{frame}{Conclusions and Future Work}
  \begin{block}{Conclusions}
    \begin{itemize}
      \item Transfer Function to Neural Network models
      \item Neural Network modeling worked best 
    \end{itemize}
  \end{block}
  \begin{block}{Future Work}
    \begin{itemize}
      \item Test models using Hardware-in-the-Loop
      \item Create new vehicle controllers 
    \end{itemize}
  \end{block}
\end{frame}
